Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-31 tex/nusselt_paper.tex
updates to figures and minor text fixes

After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible Nu is retrieved.  
Nusselt numbers for
all simulations at low and high Ma are plotted in Fig. \ref{fig:nu_v_ra}.  At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $Nu \propto Nu^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($Ra \leq 10^4$), the scaling of $Nu$ with $Ra$ is inflated, with $Nu \propto Ra^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $Nu \propto Ra^{0.19}$.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado’s George 
Ellery Hale Graduate Student Fellowship.
This work was supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center
with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

>>>>

After appropriately time-averaging the fluxes for $\geq 200 t_b$, a sensible flux average is retrieved.  
Nusselt numbers for
all simulations at low and high Ma are plotted as a function of Ra in Fig. \ref{fig:nu_v_ra}.  
At $\epsilon = \{10^{-4}, 10^{-7}\}$,
scaling laws of $\text{Nu} \propto \text{Ra}^{\{0.31, 0.31\}}$ are retrieved.  At $\epsilon = 0.5$, in the near-sonic
regime ($\text{Ra} \leq 10^4$), the scaling of Nu with Ra is inflated, with $\text{Nu} \propto \text{Ra}^{0.45}$.  As simulations
pass into the supersonic regime and shocks start to form near the downflows,
that scaling drops to $\text{Nu} \propto \text{Ra}^{0.19}$.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center
with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
